Thermodynamic fragments for magic states in quantum computation

### 2021-02-25 magic_paper.tex
More tidying before the unital section

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
We highlight the defining property of a monotone here, as it is useful in several sections that follow.
\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
    Let $\R = (\F, \O)$ be a resource theory.
    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
    \begin{equation}
        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
    \end{equation}
\end{definition}
The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right).
    \end{equation}
    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
\end{definition}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.

@@

Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
\end{equation}
where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.

@@

\subsection{Majorization computations in $\sigma$--fragments}

It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
The curves in the figure are constructed in the \emph{unital fragment}, i.e. the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$.
In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{RECAST}
    }
    \label{fig:lctoy}
\end{figure}
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}n$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$; \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$.    
    \nick{change / move / remove ?}
    }%
    \label{fig:lcs}
\end{figure}

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
As a consequence, checking whether a magic state conversion of the form
\begin{equation}
	\rho \xrightarrow{\E \in \O_\sigma} \tau
\end{equation} 
is possible, reduces to the set of constraints
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
\end{equation}
due to~\cref{thm:sigmamajor,thm:dmajor}.

@@

The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}
\nick{should we include the area? Have a look at~\cref{app:areamono}}

@@

We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
	We choose the index mapping so that the vector of component ratios, 
	\begin{equation}
		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
	\end{equation}
	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Let $i_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
	Then, $(\W{\rho})_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
	\begin{equation}
		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} (\W{\rho})_i,
	\end{equation}
	and is achieved at
	\begin{equation}\label{eq:maxloc}
		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} (\W{\sigma})_i.
	\end{equation}

@@

We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
Conversely, the maximum of the Lorenz curve acts as a valid magic monotone.
This implies the following result.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

\section{Magic in the unital fragment}\label{sec:unital}
The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
Operations in $\rcu$ can be expressed as
\begin{equation}
    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d.
\end{equation}
Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
In this case, the majorization condition~(\ref{eq:majbound}) needs to be checked in all the $\sigma$--fragments that reflect the symmetries of the operation sequence.

@@

In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
\nick{Explain asymptotic behaviour?}
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill.pdf}
    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:dist} with $\epsilon' = 0.05$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities. 
    \nick{Redo figure}
    }
    \label{fig:unital_distill}
\end{figure}

\iffalse
% Copies plot
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill_copies.pdf}
    \caption{\textbf{Copies required for Strange state distillation.} Mana and Lorenz curve copy thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
    Lorenz curve comparison consistently provides higher low bounds on the number of noisy Strange state copies required.
    }
    \label{fig:unital_distill_copies}
\end{figure}
\fi

\null\newpage

@@

We would now like to study the constraints coming solely from majorization in the unital fragment. 
Define the $\epsilon$-noisy Strange state $\ketbra{\rm{S}}$,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.

We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}n$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$. 
Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it. More precisely the associated Lorenz curve in invariant under tensoring in arbitrary many copies of this free state.
This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
\begin{equation}\label{eq:sudist}
	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(n', \epsilon', n - n') \coloneqq  \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
\end{equation}
where all copies $n, n', n - n'$ are even.
Since the initial state can be written in the form $\rho_{\rm{S}}(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}(x)$ for the generic noisy strange state $\rho_{\rm{S}}(n, \epsilon ,n')$.
This curve is defined at $9^n$ points between $0$ and $1$.
The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
The full details are provided in~\cref{app:lcsu_technical}.

@@

\newpage
\section{Magic bounds in arbitrary stabilizer fragments}\label{sec:thermal}

>>>>

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.

The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the vector of ratios between the corresponding components of $\bmw$ and $\bmd$.

    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
    \end{equation}
    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
\end{definition}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.

@@

Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
\end{equation}
where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
\begin{equation}
	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
\end{equation}
The correspondence between the phase space and pure vector representations of the Wigner distribuition is discussed more in~\cref{app:cmpairs}.

@@

\subsection{Lorenz curves of quasi-probabilities in $\sigma$--fragments}

It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve and defined as
\begin{equation}
	\widetilde{w}(\rho|\sigma)_i \coloneqq \frac{w(\rho)_i}{w(\sigma)_i},
\end{equation}
is called the Gibbs-rescaled distribution of $\rho$ with respect to $\sigma$.

An example of comparison between different Lorenz curves is provided in~\cref{fig:lctoy}.
The curves in the figure are constructed in the \emph{unital fragment}, i.e. the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$ whose Wigner distribution is the uniform probability distribution.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{\textbf{Quasi-probability Lorenz curve comparison}.
    The Lorenz curves are constructed by the Wigner distributions illustrated in~\cref{fig:wstate_examples} in the unital fragment $\O_{\id/d}$ for $d=3$.
    The maximally mixed state curve is simply the line connecting $(0,0)$ and $(1,1)$.
    There is no operation in $\O_{\id/d}$ that can convert $\ket{\rm{S}}$ to $\ket{0}$, as their Lorenz curves intersect.
    }
    \label{fig:lctoy}
\end{figure}

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
As a consequence, checking whether a magic state conversion of the form
\begin{equation}\label{eq:sigma_conv}
	\rho \xrightarrow{\E \in \O_\sigma} \tau
\end{equation} 
is not possible, reduces to the set of constraints
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
\end{equation}
due to~\cref{thm:sigmamajor,thm:dmajor}.

@@

The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}
\nick{should we include the area? Have a look at~\cref{app:areamono}}

@@

We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	We may use the vector notation of the Wigner distributions $\bmw(\rho)$ and $\bmw(\sigma)$.
	We choose the component indexing so that the Gibbs-rescaled distribution 
	\begin{equation}
		\widetilde{\bm{w}}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
	\end{equation}
	is sorted, $\widetilde{\bm{w}} = \widetilde{\bm{w}}^\downarrow$.
	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.

	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bm{w}}^\downarrow$.
	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
	\begin{equation}
		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
	\end{equation}
	and is achieved at
	\begin{equation}\label{eq:maxloc}
		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
	\end{equation}

@@

We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
Conversely, it is now clear that the maximum of the Lorenz curve acts as a valid magic monotone.
This implies the following result.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

In the sections~\cref{sec:unital,sec:stab}, we study majorization constraints on magic distillation arising in different fragments. 
For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
\end{equation}
in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform. 
For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.

In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
As shown in~\cref{lem:lcmax}, the curve peaks equal $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$ independently of the $\sigma$--fragment.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of $n$-copy Strange states.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$; \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$.    
    \nick{change / move / remove ?}
    }%
    \label{fig:lcs}
\end{figure}

\null\newpage
\null\newpage

\section{Magic in the unital fragment}
\label{sec:unital}

The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
Operations in $\rcu$ can be expressed as
\begin{equation}
    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d.
\end{equation}
Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
In such a case, the majorization condition~(\ref{eq:majbound}) needs to be checked in the $\sigma$--fragments that reflect all symmetries of the operation sequence.

@@

@@

We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \leq \epsilon$ and $n' \leq n$,
\begin{equation}\label{eq:sudist}
	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
\end{equation}
where all copies $n, n', n - n'$ are even.
Since the state $\frac{1}{3} \id$ is free, tensoring in copies of it does not affect the distillation process.

Since the initial state can be written in the form $\rho_{\rm{S}}(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}(x)$ for the generic noisy strange state $\rho_{\rm{S}}(n, \epsilon ,n')$.
This curve is defined at $9^n$ points between $0$ and $1$.
The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
The full details are provided in~\cref{app:lcsu_technical}.

@@

\newpage
\section{Magic bounds in arbitrary stabilizer fragments}
\label{sec:stab}
